\section{Manual Paramter Tuning}

\textcolor{red}{
Perform some manual tuning of relevant algorithmic parameters to find sensible parameter settings
for the final experiments. Relevant parameters may be related to the degree of randomization,
neighborhood structure sizes, probabilities for the random step function in composite neighborhood
structures, the cooling schedule, the tabu list length and its variation, etc. Report the impact of a
number of different settings on the solution quality of a selected meaningful subset of instances.}

\pagebreak

\section{Delta Evaluation}

\textcolor{red}{Use delta-evaluation.
Explain which steps in your algorithm use delta-evaluation and describe
why delta-evaluation results in better performance in this step. Are there other elements in your
algorithm that could have also benefitted from delta-evaluation?}

\section{Delta Evaluation}

We implemented delta evaluation, but we only did so for one case to have a working example with an estimate of 
the performance gain and a proof of correctness.\\
Since the structure of our functions did not really fit delta evaluation, we created new, adapted functions. 
The basic idea behind our delta evaluation is that for every changed bit in $A$ we calculated the added cost 
similar to the following pseudocode:\\

\begin{verbatim}
    changed = (G.A[i, j] == 1)
    G.A[i, j] = 0
    cost_reduced = (G.A0[i, j] == 0)
    added_cost += changed * (-cost_reduced * 2 + 1) * G.W[i,j]
\end{verbatim}

We adapted the move operators \texttt{fuse\_first!} and \texttt{swap\_first!}, you can find the adapted versions 
in \texttt{move\_ops\_delta.jl}. We made a new version of the VND which you can find in \texttt{metaheuristics.jl}, 
it is called \texttt{vnd\_delta!}.\\

We only did a quick check on the performance and correctness of our implementation of delta evaluation in 
\texttt{delta\_eval.jl}. If you run it you will see, that the improvement that delta evaluation made was 
(if at all existend) smaller than statistical fluctuations of the runtime. On our machine it takes 50 seconds 
to run, if you dont want to run it, the output of our machine is: (for one run, the time, of course, fluctuates 
statistically)

\begin{verbatim}
    ======
    Demo of Delta Evaluation
    ======
    running vnd and vnd_delta for file ../data/datasets/inst_competition/heur051_n_300_m_20122.txt
    
    Profiler of VND with fastest configuration with delta evaluation
    calculated obj value of delta evaluation is: 6930
    Actual obj value is: 6930
    Total time for VND is 3.578387975692749
    ====
    
    
    Profiler of VND with fastest configuration without delta evaluation
    Actual obj value is: 6930
    Total time for VND is 3.64827299118042
    ====
\end{verbatim}

We know that this is not good practice in terms of experimentation but we think it is sufficient to show 
that delta evaluation is correct and for this problem not very useful. We also ran this for other files, the 
results were comparable.\\